---
title: "Cleaning the Combined BI And Survey Career Data"
author: "Ri'ann Yates-Miller"
output:
  html_document:
    date: "`r format(Sys.time(), '%d %B, %Y')`"
    code_folding: hide
    df_print: paged
    number_sections: yes
    theme: cerulean
    toc: yes
    toc_float: yes
    code_download: true
  word_document:
    toc: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message=FALSE,warning=FALSE)

#package intialization
rm(list = ls()) # clear global environment
graphics.off() # close all graphics
if(require(pacman)==FALSE) install.packages("pacman")
pacman::p_load(DataExplorer,tidyverse,readxl,zoo,stargazer,kableExtra,skimr,plotly,ggpubr,vtable,tm, fastDummies)
```

# Introduction and Purpose

Write something here 
~ business value prop here probably

# Data Sources

Write something here

## Read in the data

```{r}
data=readRDS(file = "FSB_BI_Survey_2019_2021.rds")
```

# Introductory EDA

Describing each data preprocessing step with small chunks of code, output where necessary, and documentation


```{r}
introduce(data)
```

```{r}
plot_intro(data)
```

```{r}
plot_missing(data)
```

```{r}
plot_histogram(data$survey_salary)
```

```{r}
plot_bar(data$survey_plans)
```

```{r}
plot_bar(data$survey_internships)
```



## Variables we want to use

Why we chose said variables (either to control or test)

### subsetting data

```{r}
data = data |> 
  dplyr::select(year.x, GPA.Range, major1, major2, survey_plans, survey_internships, survey_salary, Gender, IPEDS.Race.Ethnicity, latin_honors, `Combined Bacc and Masters`, survey_state)
```

### changing data types
```{r}
data$year.x = as.factor(data$year.x)
data$GPA.Range = as.factor(data$GPA.Range)
data$survey_plans = as.factor(data$survey_plans)
data$Gender = as.factor(data$Gender)
data$IPEDS.Race.Ethnicity = as.factor(data$IPEDS.Race.Ethnicity)
data$`Combined Bacc and Masters` = 
  as.factor(data$`Combined Bacc and Masters`)

## if the variables aren't encoded here they will be encoded later in the analysis
```

# Data Preprocessing

blurb for presentation

## Location Cleaning

Controlling for location, had to be cleaned~~


## Major1 Cleaning

inconsistencies such as: 
~~

```{r}
unique(data$major1)
```

### Management and Leadership v. Human Capital Mgmt & Leadership v. Management and Organizations

```{r}
library(dplyr)

# Apply the correction selectively
data = data %>%
  mutate(major1 = ifelse(major1 %in% c("Management and Leadership", "Management and Organizations", "Human Capital Mgmt& Leadership"), "Human Capital Mgmt & Leadership", as.character(major1)))

# Verify the results
unique(data$major1)

```

### What is Interdisciplinary Business Management --\> is a thing but I don't think it's a thing anymore

Only 13 observations and no salary data. Will skew analyses

```{r}
data = data[data$major1 != "Interdisciplinary Bus Managemt", ]
```


### Entrepreneurship can only be a co-major or minor --\> should include major two?

Including all major 2's adds a lot of levels. Maybe not every co-major combo, but I feel like Entrepreneurship is an important one, since it literally cannot be a single major


```{r}
data[data$major1 == "Entrepreneurship", c("major1", "major2")] <- data[data$major1 == "Entrepreneurship", c("major2", "major1")] 
```


### What's general business --\> undecided

Only one row and almost all of that data is NA  --> drop
```{r}
data = data[data$major1 != "General Business", ]
```

## Salary 
```{r}
  data=data |> 
  dplyr::group_by(major1) |>
  mutate(survey_salary=replace(survey_salary,is.na(survey_salary), mean(survey_salary,na.rm=T)))
```

## Internship Condensing

Why we want to separated internships into 0, 1, More than 1~~> easier to interpret
```{r}
data$survey_internships = ifelse(
  (data$survey_internships != "0") & (data$survey_internships != "1"), 
  'Over 1', 
  data$survey_internships)
```

```{r}
data$survey_internships = as.factor(data$survey_internships)
```

## GPA Condensing

Why we want to separated GPA into Low, Med, High


## Making Latin Honors Binary

Why we want to make this binary~~
```{r}
data$latin_honors = ifelse(
  data$latin_honors != "0", 
  1, 
  0)
```

```{r}
data$latin_honors = as.factor(data$latin_honors)
```

## Making Major2 Binary

Why we want to make this binary~~ (something to control for)
```{r}
data$major2 = ifelse(
  data$major2 != "none", 
  1, 
  0)
```

```{r}
data$major2 = as.factor(data$major2)
```

## Drop remaining NAs
internship and fulltime. Important to our analysis and hard to imputate without skewing or missrepresenting the data, so drop. Went from 3222 to 1828 (if we include state)

```{r}
data = data |> na.omit()
```


# Conclusion

~~data's cleaning ready for analysis
